### 2023-11-08 Scripts/Manuscript/manuscript.Rmd
added replication ratio table with not right formatting and stopped some output from appearing in code.

```{r Hypothesis 1 Model}
# first some descriptives of reliability reporting
# Measurement type per original and replication:
H1_descriptive_table_1 <- table(data_h1$rep_org, data_h1$N_items)

@@

```{=tex}
\begin{align*}
& Level 1: alpha_{ij} = \beta_{0j} + e_{ij} \qquad\qquad\quad e_{ij} \sim N(0, \sigma_{e}^{2}) \\
& Level 2: \beta_{0j} = \gamma_{00} + u_{0j} \qquad\qquad\qquad u_{0j} \sim N(0, \sigma_{u0}^{2}) \\
& Mixed: alpha_{ij} = \gamma_{00} + u_{0j} + e_{ij}
\end{align*}
```
```{r Hypothesis 2 Model}
# intercept only model to check the within and between group variance.
H2_test_result_alpha <- summary(lmer(formula = alpha ~ 1 + (1|g), data = data_h2))

@@

```{r ICC calculations}
# alpha
# within group variance: 0.04384
# between group variance: 0.19824
ICC_alpha <- 0.19824 / (0.04384 + 0.19824)

@@

```{r Hypothesis 3 Main Test}
## The main model to test hypothesis 3, through a logistic regression model.
H3_test_result_main_alpha <- summary(glm(formula = replication ~ 1 + alpha_avg, 
                                     family = binomial(), data = data_h3_avg))

@@

```{r Hypothesis 3 Multilevel Model Sensitivity Analyses}
## sensitivity analyses.
# running a random intercept multilevel logistic model
H3_test_result_int_sensitivity_alpha <- summary(glmer(formula = replication ~ 1 
                                                + alpha + (1|g), family = 
                                                binomial(), data = 
                                                data_h3_multiple))

@@

```{r Hypothesis 4 Model}
## Hypothesis 4 beta regression model
# running the model with none revised QMP ratio's
H4_test_results <- betareg(QMP_ratio ~ rep_org, data = data_h4)

@@

```{r Hypothesis 5 Model}
## Hypothesis 4 beta regression model
H5_test_results <- betareg(QMP_ratio ~ hypothesis_support, data = data_h5)

@@

```{r Hypothesis 6 Model}
H6_test_results <- betareg(Rep_QMP_ratio ~ QMP_ratio, data = data_h6)

@@

```{r Hypotheses 5 & 6 Sensitivity Analyses}
## Hypothesis 5 sensitivity test using a random intercept Guassian model.
# create dummy H5 dataframe for use in sensitivity test
data_h5_sens <- data_h5

@@

```{r Hypothesis 6 Associations}
## Associations between the QMP categories
# associations are generated using a helper function available in the source_ 
# script. These associations correspond to the coefficients between replication
# and original article QMPs of the various QMP types, as estimated through a 
# beta regression.
# Associations between the QMP categories (original QMP coding)
Results_H6_between <- Associations_H6(data_h6)

@@

```{r Unidimensionality Exploratory Analysis}
extracted_data_list <- list(data_1.10_clean, data_1.11_clean, data_1.12.3.1_clean,
                            data_1.12.3.2_clean, data_2.10.1_clean,
                            data_2.12.1_clean, data_2.12.2_clean, 
                            data_2.12.3_clean, data_2.15_clean, data_2.20_clean,
                            data_2.23_clean, data_3.2.1.1_clean, 
                            data_3.2.1.2_clean, data_3.7.1_clean, 
                            data_3.7.2_clean, data_3.8.2_clean,
                            data_5.1.1_clean, data_5.7_clean, data_5.9.1_clean)

@@

```{r Code for Descriptives Retrieval}
N_replications <- mean(coded_data_replications$N, na.rm = TRUE)
IQR_replications <- IQR(coded_data_replications$N, na.rm = TRUE)
N_original <- mean(coded_data_original_shortened$N, na.rm = TRUE)
IQR_original <- IQR(coded_data_original_shortened$N, na.rm = TRUE)

N_h_support <- table(coded_data_replications$hypothesis_support)["Yes"]
N_measures <- nrow(coded_data_replications)
```

The mean sample size within the replications was `r apa_num(N_replications, digits = 0)` participants (IQR = `r apa_num(IQR_replications, digits = 0)`). In the original articles the mean sample size was `r apa_num(N_original, digits = 0)` (IQR = `r apa_num(IQR_original, digits = 0)`). In total, support was found for hypothesized effects of `r apa_num(N_h_support, digits = 0)` of the `r apa_num(N_measures, digits = 0)` measures. Proportions of replication success per Many Labs project can be found in Table XXX.

>>>>

```{r Hypothesis 1 Model, include = FALSE}
# first some descriptives of reliability reporting
# Measurement type per original and replication:
H1_descriptive_table_1 <- table(data_h1$rep_org, data_h1$N_items)

@@

```{=tex}
\begin{align*}
& Level 1: alpha_{ij} = \beta_{0j} + e_{ij} \qquad\qquad\quad e_{ij} \sim N(0, \sigma_{e}^{2}) \\
& Level 2: \beta_{0j} = \gamma_{00} + u_{0j} \qquad\qquad\qquad u_{0j} \sim N(0, \sigma_{u0}^{2}) \\
& Mixed: alpha_{ij} = \gamma_{00} + u_{0j} + e_{ij}
\end{align*}
```
```{r Hypothesis 2 Model, include = FALSE}
# intercept only model to check the within and between group variance.
H2_test_result_alpha <- summary(lmer(formula = alpha ~ 1 + (1|g), data = data_h2))

@@

```{r ICC calculations, include = FALSE}
# alpha
# within group variance: 0.04384
# between group variance: 0.19824
ICC_alpha <- 0.19824 / (0.04384 + 0.19824)

@@

```{r Hypothesis 3 Main Test, include = FALSE}
## The main model to test hypothesis 3, through a logistic regression model.
H3_test_result_main_alpha <- summary(glm(formula = replication ~ 1 + alpha_avg, 
                                     family = binomial(), data = data_h3_avg))

@@

```{r Hypothesis 3 Multilevel Model Sensitivity Analyses, include = FALSE}
## sensitivity analyses.
# running a random intercept multilevel logistic model
H3_test_result_int_sensitivity_alpha <- summary(glmer(formula = replication ~ 1 
                                                + alpha + (1|g), family = 
                                                binomial(), data = 
                                                data_h3_multiple))

@@

```{r Hypothesis 4 Model, include = FALSE}
## Hypothesis 4 beta regression model
# running the model with none revised QMP ratio's
H4_test_results <- betareg(QMP_ratio ~ rep_org, data = data_h4)

@@

```{r Hypothesis 5 Model, include = FALSE}
## Hypothesis 4 beta regression model
H5_test_results <- betareg(QMP_ratio ~ hypothesis_support, data = data_h5)

@@

```{r Hypothesis 6 Model, include = FALSE}
H6_test_results <- betareg(Rep_QMP_ratio ~ QMP_ratio, data = data_h6)

@@

```{r Hypotheses 5 & 6 Sensitivity Analyses, include = FALSE}
## Hypothesis 5 sensitivity test using a random intercept Guassian model.
# create dummy H5 dataframe for use in sensitivity test
data_h5_sens <- data_h5

@@

```{r Hypothesis 6 Associations, include = FALSE}
## Associations between the QMP categories
# associations are generated using a helper function available in the source_ 
# script. These associations correspond to the coefficients between replication
# and original article QMPs of the various QMP types, as estimated through a 
# beta regression.
# Associations between the QMP categories (original QMP coding)
Results_H6_between <- Associations_H6(data_h6)

@@

```{r Unidimensionality Exploratory Analysis, include = FALSE}
extracted_data_list <- list(data_1.10_clean, data_1.11_clean, data_1.12.3.1_clean,
                            data_1.12.3.2_clean, data_2.10.1_clean,
                            data_2.12.1_clean, data_2.12.2_clean, 
                            data_2.12.3_clean, data_2.15_clean, data_2.20_clean,
                            data_2.23_clean, data_3.2.1.1_clean, 
                            data_3.2.1.2_clean, data_3.7.1_clean, 
                            data_3.7.2_clean, data_3.8.2_clean,
                            data_5.1.1_clean, data_5.7_clean, data_5.9.1_clean)

@@

The mean sample size within the replications was `r apa_num(mean(coded_data_replications$N, na.rm = TRUE), digits = 0)` participants (IQR = `r apa_num(IQR(coded_data_replications$N, na.rm = TRUE), digits = 0)`). In the original articles the mean sample size was `r apa_num(mean(coded_data_original_shortened$N, na.rm = TRUE), digits = 0)` (IQR = `r apa_num(IQR(coded_data_original_shortened$N, na.rm = TRUE), digits = 0)`). In total, support was found for hypothesized effects of `r apa_num(table(coded_data_replications$hypothesis_support)["Yes"], digits = 0)` of the `r apa_num(nrow(coded_data_replications), digits = 0)` measures. Proportions of replication success per Many Labs project can be found in Table XXX.

```{r Replication Ratio Table}
# construct the replication ratio table to be printed
replication_ratio_table <- data.frame("Many Labs Version" = c("1", "2", "3", "5", "Total"),
                                      "N Total" = c(table(coded_data_replications$many_labs_version), nrow(coded_data_replications)), 
                                      "N Replicated" = c(table(coded_data_replications$many_labs_version, coded_data_replications$hypothesis_support)[, "Yes"], table(coded_data_replications$hypothesis_support)["Yes"]))

# calculate the replication ratio from the N measures whose studies were replicated
# and the N total measures, per Many Labs study.
replication_ratio_table$"Replication Ratio" <- replication_ratio_table$N.Replicated / replication_ratio_table$N.Total

# print the table in apa formatting
apa_table(
  replication_ratio_table, align = c("l", "r", "r", "r")
  , caption = "Ratio of measures for which the effect was considered replicated, across many labs projects"
  , note = "AWITHSUPERSCRIPT replication was assessed as unclear for three of the measures, since their effect was not fully replicated. These have been treated as not replicated within this table and further analyses throughout the thesis"
  , escape = TRUE, placement= "h")

### add a midrule before total
